\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-17 article.tex
merged part on causality

% Introduce notation + goal in mathematical score
The connectomes, the neural network, is represented by a (un)directed graph $G = (V, E)$ comprising
a set of nodes $V$ and a set of edges $E \subseteq \left\{(i, j) \in V \times
V\right\}$, (un)ordered pair from $V$.
Each node $i \in V$ represents a neuron, and each edge $(i, j) \in E$
represents a direct link and interactions between neuron $i$ and a neuron $j$.
In the directed graph, each edges also expresses a causal relationship: an
edge $(i, j) \in E$ indicates that the state of neuron $j$ might be caused
by the neuron $i$. The network inference task is set as follows :
\textit{Given the observations $(x^t \in \mathcal{R}^{|V|})_{t=1}^T $
along $T$ periods of time of the $|V|$ neurons, the goal is to infer the
adjacency matrix $A : a_{i,j} = \mathbb{1}((i, j) \in E)$ of the neural network
of graph $G$, where $\mathbb{1}$ is the indicator function.}

The directivity in the network introduce causal relations through neurons. A
directed edge, i.e. $a_{i,j} = 1$ and $a_{j,i} = 0$, means that neuron $i$
causes $j$. The causal mechanism implies that when neuron $i$ is active, also
denoted in this paper as a firing event or a burst, neuron $j$ may be
afterwards activated consequently. Let us notice that neuron $j$ depends on
all its ancestors and its activation may not be as straightforward as we may
think if the causal activation is not systematic (stochastic?). The reciprocal
phenomenon is only possible when the edge is bidirectionnal, i.e. $a_{i,j} =
a_{j,i} = 1$.

>>>>

% Introduce notation + goal in mathematical score
The connectomes, the neural network, is represented by a (un)directed graph
$G = (V, E)$ comprising
a set of nodes $V$ and a set of edges $E \subseteq \left\{(i, j) \in V \times
V\right\}$, (un)ordered pairs from $V$.
Each node $i \in V$ represents a neuron, and each edge $(i, j) \in E$
represents a direct link and interaction between neuron $i$ and $j$.
In the directed graph, edges also express causality: the
state of a neuron $i$ might be due to the state of one or several of its
parents $\left\{j : (j, i) \in E, j \in V\right\}$.
The network inference task is set as follows :
\textit{Given the observations $(x^t \in \mathcal{R}^{|V|})_{t=1}^T $
along $T$ periods of time of the $|V|$ neurons, the goal is to infer the
adjacency matrix $A : a_{i,j} = \mathbb{1}((i, j) \in E)$ of the neural network
of graph $G$, where $\mathbb{1}$ is the indicator function.}
